The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-05 paper/ms.tex
Add other Ji distributions to appendix

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{fig/schmactions_Jz_zerr_hist.pdf}
\end{center}
\caption{A histogram of the observed values in $J_z$ for the thick-disk (top panel) and thin-disk (bottom panel) orbits
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account. Intuition for the shape
of each panel is given in the text. We also plot one half the 95\uth{}
percentile minus the 5\uth{} percentile of each distribution as a horizontal
arrow anchored on the true $J_z$ value. We call this $\Delta J_z$ and will use
it (along with the similarly defined $\Delta J_R$ and $\Delta J_{\phi}$) to
empirically describe the error distribution. We see that $\Delta J_z$ roughly
corresponds to the distance from the true $J_z$ value to one of the modes of
the distribution of observed $J_z$ values.}
\label{fig:Jz_hist}
\end{figure}

@@

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{fig/schmactions_Jz_zerr_hist.pdf}
\end{center}
\caption{A histogram of the observed values in $J_z$ for the thick-disk (top panel) and thin-disk (bottom panel) orbits
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account. Intuition for the shape
of each panel is given in the text. We also plot one half the 95\uth{}
percentile minus the 5\uth{} percentile of each distribution as a horizontal
arrow anchored on the true $J_z$ value. We call this $\Delta J_z$ and will use
it (along with the similarly defined $\Delta J_R$ and $\Delta J_{\phi}$) to
empirically describe the error distribution. We see that $\Delta J_z$ roughly
corresponds to the distance from the true $J_z$ value to one of the modes of
the distribution of observed $J_z$ values. Similar plots for $J_R$ induced by
a $z$ offset and $J_R$ and $J_{\phi}$ induced by an $x$ offset are given in
Appendix~\ref{app:hist}.}
\label{fig:Jz_hist}
\end{figure}

@@

In Appendix~\ref{app:hist} we plot the same histogram as in
Figure~\ref{fig:Jz_hist}, but for the observed distributions of $J_R$ induced
by a $z$ offset (upper left panel of Figure~\ref{fig:many_orbit_wrong_ref})
and the observed distributions of $J_R$ and $J_{\phi}$ errors induced by an
$x$ offset (lower left and lower center panels of
Figure~\ref{fig:many_orbit_wrong_ref}, respectively). We find similar error
distributions as in Figure~\ref{fig:Jz_hist}, with the exception that the
observed $J_R$ distribution induced by an $x$ offset more closely resembles a
Gaussian.

@@

\section{$J_R$ and $J_{\phi}$ Observed Distributions} \label{app:hist}

In Figure~\ref{fig:JR_zerr_hist} we plot the observed $J_R$ distribution
induced by an offset in $z$, and in Figures~\ref{fig:JR_xerr_hist} and
\ref{fig:Jphi_xerr_hist} we plot the observed $J_R$ and $J_{\phi}$
distributions induced by an offset in $x$. We plot the distributions for the
thick-disk (top panels) and thin-disk (bottom panels) orbits.

We find that the observed $J_R$ distribution induced by an offset in $x$ more
closely resembles a Gaussian, while the observed $J_R$ distribution induced by
an offset in $z$ and the observed $J_{\phi}$ distribution induced by an offset
in $x$ are both similar to the observed $J_z$ distribution induced by an
offset in $z$ (see Figure~\ref{fig:Jz_hist}).

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_JR_zerr_hist.pdf}
\end{center}
\caption{A histogram of the observed values in $J_R$ for the thick-disk (top
panel) and thin-disk (bottom panel) orbits assuming a $z$ offset of
$100\,\pc$. The induced error distribution more closely resembles a Gaussian
centered on the null value.}
\label{fig:JR_zerr_hist}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_JR_xerr_hist.pdf}
\end{center}
\caption{A histogram of the observed values in $J_R$ for the thick-disk (top
panel) and thin-disk (bottom panel) orbits assuming a $x$ offset of
$100\,\pc$. The induced error distribution is non-Gaussian and bimodal, with
neither of the modes centered on null.}
\label{fig:JR_xerr_hist}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_Jphi_xerr_hist.pdf}
\end{center}
\caption{A histogram of the observed values in $J_{\phi}$ for the thick-disk (top
panel) and thin-disk (bottom panel) orbits assuming a $z$ offset of
$100\,\pc$. The induced error distribution is non-Gaussian and bimodal, with
neither of the modes centered on null.}
\label{fig:Jphi_xerr_hist}
\end{figure}
